---
title: 'Homework 10: Data from the Web'
output: github_document
---

### Load packages

Load necessary packages.

```{r message=FALSE}
library(tidyverse)
library(magrittr)
library(purrr)
library(glue)
library(stringr)
library(rvest)
library(xml2)
library(ggplot2)
library(knitr)
```

## Scrape data

### Billboard The Hot 100

Extract data from [Billboard The Hot 100](https://www.billboard.com/charts/hot-100). 

```{r}
hot_100 <- read_html("https://www.billboard.com/charts/hot-100")
```

### Song name

Let's get a list of the top 10 song names!

```{r}
song_name <- hot_100 %>% 
  html_nodes(".chart-row__song") %>% 
  html_text()

head(song_name, 10)
```

### Artist name

Extract a list of the corresponding arist names.

```{r}
artist_name <- hot_100 %>% 
  html_nodes(".chart-row__artist") %>% 
  html_text()

head(artist_name, 10)
```

We will remove the leading and trailing whitespace.

```{r}
artist_name_mod <- hot_100 %>% 
  html_nodes(".chart-row__artist") %>% 
  html_text() %>% 
  trimws(which = c("both")) ## remove leading and trailing whitespace

head(artist_name_mod, 10)
```

### Ranking

Let's look at the current ranking for each song.

```{r}
current_week <- hot_100 %>% 
  html_nodes(".chart-row__current-week") %>% 
  html_text()

head(current_week, 10)
```

### Weeks on Chart

Let's also look at the number of weeks the song has been on the chart.

```{r}
weeks_on_chart <- hot_100 %>% 
  html_nodes(".chart-row__weeks-on-chart") %>% 
  html_text()

head(weeks_on_chart, 10)
```

We will extract the week on charts value.

```{r}
weeks_on_chart_mod <- hot_100 %>% 
  html_nodes(".chart-row__weeks-on-chart") %>% 
  html_text() %>% 
  str_sub(-3,-2) %>% ## extract weeks on chart value
  trimws(which = c("both")) ## trim whitespace for single digits

head(weeks_on_chart_mod, 10)
```

### Dataframe

We can put our data together into a data frame. Let's take a look at the top 40 hits!

```{r}
song_df <- data.frame(Ranking = as.numeric(current_week), ## convert to numeric
                      Weeks_on_chart = as.numeric(weeks_on_chart_mod), ## convert to numeric
                      Song = song_name,
                      Artist = artist_name_mod)

song_df %>% 
  head(40) %>% ## top 40 songs
  kable()
```


### Data analysis

Plot the top 20 songs to the number of weeks it's been on the chart.

```{r}
song_df %>% 
  head(20) %>% 
  ggplot(aes(x=Song, y=Weeks_on_chart)) +
  geom_point(shape=21, aes(size=Ranking, fill=Ranking)) +
  theme_bw() +
  labs(title = "Top 20 Hits vs. Weeks on Chart",
       fill = "Ranking",
       size = "Ranking",
       x = "Song Name",
       y = "Weeks on Chart") +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle=45, hjust=1)) +
  scale_fill_distiller(palette="YlGnBu")
```

It makes sense that the mid ranked songs have been on the charts longer. People lose interest and want to hear new music!

Let's look at that comparison closely!

```{r}
song_df %>% 
  ggplot(aes(x=Ranking, y=Weeks_on_chart)) +
  geom_col(fill="pink", colour="white") +
  theme_bw() +
  labs(title = "Ranking vs. Weeks on Chart",
       x = "Ranking",
       y = "Weeks on Chart") +
  theme(plot.title = element_text(hjust=0.5))

```

Confirmed! Songs ranked around 25-50 have been on the charts for the longest period of time. Almost 6 months to a year! The songs at the bottom of the chart are probably new releases, slowly making their way up the charts.




