---
title: 'STAT547 Homework 06: Data wrangling wrap up'
output: github_document
---

### Load packages

Load necessary packages.

```{r message=FALSE}
library(tidyverse)
library(stringr)
library(knitr)
library(gapminder)
library(testthat)
library(ggplot2)
library(MASS)
```


## 2. Writing functions

Write a function to compute the robust regression of life expectancy on year with the Gapminder data. `MASS::rlm()` will be used.

#### Practice with some data

Extract data for one country to interactively work with the code.

```{r}
p_country <- "Canada"
p_dat <- gapminder %>%
    filter(country == p_country)

kable(p_dat)
```

Plot the data to see what it looks like!

```{r}
p <- ggplot(p_dat, aes(x = year, y = lifeExp))
p + geom_point() + geom_smooth(method = "rlm", se = FALSE) + theme_bw()
```


#### Practice with working code

Fit the robust regression.

```{r}
p_fit <- rlm(lifeExp ~ year, p_dat)
coef(p_fit)
```

Hmm... it doesn't seem quite right that life expectancy was about -358. Let's make this more appropriate and set life expectancy to the earliest year in Gapminder (1952).

```{r}
p_fit <- rlm(lifeExp ~ I(year - 1952), p_dat)
coef(p_fit)
```

#### Turn the working code into a function!

```{r}
robust_fit <- function(dat, offset = 1952) {
  the_fit <- rlm(lifeExp ~ I(year - offset), dat)
  setNames(coef(the_fit), c("intercept", "slope"))
}
robust_fit(p_dat)
```

Hooray, we get the same result as above!

#### Test the function on other data

Let's look at the robust regression of life expectancy on year in Algeria.

```{r}
p_country2 <- "Algeria"
p_dat2 <- gapminder %>%
    filter(country == p_country2)

kable(p_dat2)
```

Plot the data!

```{r}
p2 <- ggplot(p_dat2, aes(x = year, y = lifeExp))
p2 + geom_point() + geom_smooth(method = "rlm", se = FALSE) + theme_bw()
```

Use our function!

```{r}
robust_fit(p_dat2)
```

It works! This function calculates the robust regression of life expectancy on year (with the earliest year of 1952).


## 3. Work with the candy data

TASK: Compare the joy/despair scores of different types of treats. 

#### Examine the raw Candy Survey data

Bring in the raw data.

```{r}
raw <- read_csv("CANDY-HIERARCHY-2015 SURVEY-Responses.csv",
                col_types = cols(
                  Timestamp = col_datetime("%m/%d/%Y %H:%M:%S")))
```

Glimpse of the data.

```{r}
glimpse(raw)
```

#### Data wrangling

Create an ID for each participant and rename "How old are you?" to `age`.

```{r}
raw_id <- raw %>% 
  mutate(id = rownames(raw)) %>%
  rename(age = "How old are you?")
```

Clean the `age` data to be integers of data with two or less characters and drop the rows with NA.

```{r}
raw_id <- raw_id %>% 
  filter(str_length(age) <= 2) %>% 
  mutate(age = as.integer(age)) %>%
  filter(!is.na(age))
```

Select data of interest from the Candy Survey. We will look at `id`, `age`, `bubble gum`, `snickers`, `fuzzy peaches`, `kale smoothie`, and `kit kat`, and rename the treats.

```{r}
candy_data <- raw_id %>% 
  rename(bubble_gum = "[Bubble Gum]",
         snickers = "[Snickers]",
         fuzzy_peaches = "[Fuzzy Peaches]",
         kale_smoothie = "[Kale smoothie]",
         kit_kat = "[Kit Kat]") %>% 
  dplyr::select(id, age, bubble_gum, snickers, fuzzy_peaches, kale_smoothie, kit_kat)

candy_data
```

Clean up the candy data and drop all rows with NA.

```{r}
candy_data <- na.omit(candy_data)

candy_data
```


#### Exploring/Analyzing

First, let's examine the number of occurences of despair and join for bubble gum using `count()`.

```{r}
bubble_gum_count <- candy_data %>%
  count(bubble_gum) %>% 
  ## rename table headings
  rename(bubble_gum = n,
         score = bubble_gum)

bubble_gum_count
```

We see that 3218 people scored bubble gum with `despair`, and 1182 with `joy`. 

Let's look at snickers.

```{r}
snickers_count <- candy_data %>%
  count(snickers) %>% 
  ## rename table headings
  rename(snickers = n, 
         score = snickers)

snickers_count
```

We can join these two tables using `inner_join()`.

```{r}
gum_and_snickers <- inner_join(bubble_gum_count, snickers_count)

gum_and_snickers
```

Let's analyze the other treats using `count()`.

```{r}
count(candy_data, snickers)
```


```{r}
fuzzy_peaches_count <- candy_data %>%
  count(fuzzy_peaches) %>% 
  ## rename table headings
  rename(fuzzy_peaches = n,
         score = fuzzy_peaches)

kale_smoothie_count <- candy_data %>%
  count(kale_smoothie) %>% 
  ## rename table headings
  rename(kale_smoothie = n,
         score = kale_smoothie)

kit_kat_count <- candy_data %>%
  count(kit_kat) %>% 
  ## rename table headings
  rename(kit_kat = n,
         score = kit_kat)
```

We want to create a combined table with the total counts of despair and joy for each treat. 
 
```{r}
candy_scores <- plyr::join_all(list(bubble_gum_count, snickers_count, fuzzy_peaches_count,
              kale_smoothie_count, kit_kat_count),
              by='score',
              type='inner')

candy_scores
```
 
Hooray! Let's plot this data!

..... WAIT, not so soon! We need to reshape this data to properly plot it.

```{r}
candy_scores_gather <- gather(candy_scores, key = treat, value = count, bubble_gum:kit_kat)

candy_scores_gather
```

Now it's ready to plot!

```{r}
candy_scores_gather %>% 
  ggplot(aes(x = treat, y = count, fill = score)) +
  geom_bar(stat="identity", position = "dodge") +
  theme_bw()
```













