---
title: 'STAT545 Homework 06: Data wrangling wrap up'
output: github_document
---

### Load packages

Load necessary packages.

```{r message=FALSE}
library(tidyverse)
library(stringr)
library(knitr)
```

## 1. Character data

Read and work the exercises in the [Strings chapter or R for Data Science](http://r4ds.had.co.nz/strings.html).

### String Basics Exercises

**1. In code that doesn’t use stringr, you’ll often see `paste()` and `paste0()`. What’s the difference between the two functions? What stringr function are they equivalent to? How do the functions differ in their handling of NA?**

`paste()` seperates strings by spaces while `paste0()` does not seperate strings by spaces. 

```{r}
paste("fried", "chicken")
paste0("fried", "chicken")
```

They are similar to `str_c()`, where `paste0()` is more similar (does not seperate strings by spaces).

```{r}
str_c("fried", "chicken")
```

The paste functions convert NA to a string and treat it like a character vector. `str_c()` returns a missing value. 

```{r}
paste(NA, "chicken")
paste0(NA, "chicken")
str_c(NA, "chicken")
```


**2. In your own words, describe the difference between the sep and collapse arguments to str_c().**

`sep` is the string inserted between arguments, and `collapse` is the string that combines arguments into a single string.

**3. Use str_length() and str_sub() to extract the middle character from a string. What will you do if the string has an even number of characters?**

```{r}

```


**4. What does str_wrap() do? When might you want to use it?**

**5. What does str_trim() do? What’s the opposite of str_trim()?**

**6. Write a function that turns (e.g.) a vector c("a", "b", "c") into the string a, b, and c. Think carefully about what it should do if given a vector of length 0, 1, or 2.**